Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-06-11 paper/Analisis.tex
Change name of addfig in Nscatt Section, from 2dHistogram50t5. to 2dHistogram0t5.
new paragraph in Nscatt section

In order to understand the effects of rotation in the morphology of the line
 we make histograms of $<N_{scatt}>$  in function of $X_{m}$ for both the 
 central Fig.~\ref{fig:NscattHisto} and the  homogeneous distribution 
 Fig.~\ref{fig:NscattHistoHOM}. For the central distribution and for lower 
 velocities we found that for some value (put the value) of $N_{scatt}$ the 
 mayority of photons have a defined value of $X_{m}$. While for higher 
 velocities photons tend spread out in $X_{m}$(Make position analysis of 
 this photons).

For the homogeneous distribution we found the same effect but also, for 
highest velocities the mayority of the photons near the surface escape 
with much less scatterings that in the static case. This analysis let us 
conclude that rotation make photons escape with less scatterings and it 
spread out the wavelenght of the of the outgoing photons represented by $X_{m}$.

@@

\begin{figure*}
     \includegraphics[width=0.40\textwidth]{2dHistogram0t5HOM.png}
     \includegraphics[width=0.40\textwidth]{2dHistogram300t5HOM.png}    
    \caption{Histogram of $N_{scatt}$ vs $x$ for the homogeneous
      distribution, left for $V_{max}=0km/s $, right for
      $V_{max}=300km/s$ \label{fig:NscattHistoHOM}}  
\end{figure*}

\begin{figure*}
     \includegraphics[width=0.40\textwidth]{2dHistogram50t5.png}
     \includegraphics[width=0.40\textwidth]{2dHistogram300t5.png}    
    \caption{Histogram of $N_{scatt}$ vs $x$ for the Central
      distribution, left for $V_{max}=50km/s $, right for
      $V_{max}=300km/s$ \label{fig:NscattHistoHOM}}  
\end{figure*}

\subsection{Escape Fraction}
\label{sec:EF}

>>>>

In order to gain a deeper understading of these results we 2D
histograms for the number of scaterrings as a function of the outgoing
dimensionless frequency $x$. In Figure \ref{fig:Nscatt2D} we show
the results of such histogram in the case $\tau{\rm H}=10^5$ for the
static case and $V_{\rm max}=300$\kms. The upper (lower) panels show the
results for the homogeneous (central) source distribution. The color
scale is logarithmic in the number of photons at a certain value
$x-N_{\rm scatt}$. This Figure clearly support our hypothesis about
the photosphere in the homogeneous distribution, in this case most of
the photons that left with $x\sim 0$ have escaped with less than $10$
scatterings, clearly explaining the origin of a single central
peak. However, for a central distribution the situation is
different. In this case the number of scatterings remains high, on the
order of the optical depth, but the two peaks do get closer to each
other. In this situation each scattering leaves the photon closer to
the center of the line than the static case.

@@

\begin{figure*}
     \includegraphics[width=0.45\textwidth]{2dHistogram0t5HOM.png}
     \includegraphics[width=0.45\textwidth]{2dHistogram300t5HOM.png}    \\
     \includegraphics[width=0.45\textwidth]{2dHistogram0t5.png}
     \includegraphics[width=0.45\textwidth]{2dHistogram300t5.png}    
    \caption{2D histogram of $N_{scatt}$ vs $x$. The upper (lower) pannels
      show the homogeneous (central) source distribution. Left
      corresponds to the static case and the right
      $V_{max}=300km/s$. The colour scale is locarithmic\label{fig:Nscatt2D}}  
\end{figure*}

%%%%
\subsection{Escape Fraction}
\label{sec:EF}
